---
title: "STATISTICAL GENOMICS AND BIOINFORMATICS PLATFORM"
subtitle: "SAMPLE DATA ANALYSIS REPORT"
author: "Yong Won Jin"
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding){rmarkdown::render(inputFile, encoding=encoding, output_dir="/home/jin/OneDrive/SGB/events/R_for_Researchers/221115_R Markdown/REPORT/")})
output:
  officedown::rdocx_document:
    reference_docx: /home/jin/OneDrive/SGB/projects/template.docx
    page_size:
      width: 8.5
      height: 11
      orient: "portrait"
    page_margins:
      top: 0.5
      bottom: 0.5
      right: 0.5
      left: 0.5
      gutter: 0
      header: 0.25
      footer: 0.25
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  include = TRUE,
  cache = FALSE,
  dpi = 150,
  cache.lazy = FALSE
  )
```

```{r load-packages, message=FALSE, warning=FALSE, include=FALSE}
# Markdown
library(officedown)
library(officer)
# Data wrangling
library(tidyverse)
# Plotting
library(cowplot)
library(plotly)
library(factoextra)
```

```{r source-functions, include=FALSE}
source('/home/jin/OneDrive/SGB/projects/functions.R')
```

```{r coverpage-par, include=FALSE}
coverpage_par <- fp_par(
  text.align = "left", 
  padding = 0,
  padding.left = 0.63,
  padding.right = 0.63,
)
```

````verbatim

PROJECT TITLE:
Sample docx report
SYNOPSIS: 
PREPARED FOR:             R for Researchers
REPORT PREPARED BY:       Yong Won Jin
                          Statistical Genomics and Bioinformatics Platform
                          Max Rady College of Medicine
                          University of Manitoba
                          E-mail:   yong.jin@umanitoba.ca
                          Tel:    204-789-3364
TIME SPENT ON ANALYSIS:   
````
\newpage

# Table of content

<!---BLOCK_TOC--->

# List of figures

<!---BLOCK_TOC{seq_id: 'fig'}--->

# List of tables

<!---BLOCK_TOC{seq_id: 'tab'}--->


\newpage

# Project description

## Study summary

This is where I would write a *summary* about the study/project - i.e. how it came about, who is involved, research question, what types of data were delivered, etc.

## Objectives

-   List research objectives here
-   You can use asterisk or dash to make a list

# Data preparation

## Load data

For the demo, we'll just use the mtcars dataset.

```{r cars, tab.cap='First 6 rows of the mtcars dataset'}
head(mtcars)
```

# Plots and Figures

Output from plotting functions are included.

```{r barplots, fig.cap='Bar plots of mpg, cyl, disp, and hp'}
mtcars %>%
  select(mpg, cyl, disp, hp) %>%
  rownames_to_column(var='Model') %>%
  pivot_longer(cols=-Model) %>%
  ggplot(mapping=aes(x=Model,value)) +
  geom_bar(stat='identity') +
  facet_grid(name ~ ., scales='free') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## Plots

For .html output, you can include 3D interactive plots using `plotly` package.

### Principal Component Analysis

```{r 2D-PCA, warning=FALSE, fig.cap='PCA plot of car models from mtcars dataset'}
res.pca <- prcomp(mtcars)
fviz_pca_ind(res.pca,
             col.ind=as.factor(mtcars$cyl),
             addEllipses = TRUE,
             legend.title='cyl',
             repel=TRUE,
             title='')
```

# Appendix

## Code

```{r all-code}
#| ref.label=knitr::all_labels(),
#| include=TRUE,
#| echo=TRUE,
#| eval=FALSE
```

## R session info

```{r session-info, include=TRUE}
sessionInfo()
```
