---
title: "STATISTICAL GENOMICS AND BIOINFORMATICS PLATFORM"
subtitle: "SAMPLE DATA ANALYSIS REPORT"
author: "Yong Won Jin"
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding){rmarkdown::render(inputFile, encoding=encoding, output_dir="/home/jin/OneDrive/SGB/events/R_for_Researchers/221115_R Markdown/REPORT/")})
output:
  html_document:
    code_folding: 'hide'
    fig_caption: true
    toc: yes
    toc_float: yes
    toc_depth: 4
    theme: lumen
always_allow_html: yes
---

```{css toc-header, eval = TRUE, echo = FALSE}
.tocify-header {
  text-indent: initial;
}

.tocify-subheader > .tocify-item {
  text-indent: initial;
  padding-left: 20px;
}

.tocify-subheader .tocify-subheader > .tocify-item {
  text-indent: initial;
  padding-left: 30px;
}

.tocify-subheader .tocify-subheader .tocify-subheader > .tocify-item {
  text-indent: initial;
  padding-left: 40px;
}

.tocify-subheader .tocify-subheader .tocify-subheader > .tocify-item {
  text-indent: initial;
  padding-left: 50px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  include = TRUE,
  cache = FALSE,
  dpi = 150,
  cache.lazy = FALSE
  )
```

```{r load-packages, message=FALSE, warning=FALSE}
# Data wrangling
library(tidyverse)
# Plotting
library(cowplot)
library(plotly)
library(factoextra)
```

```{r source-functions}
source('/home/jin/OneDrive/SGB/projects/functions.R')
```

# Project description

## Study summary

This is where I would write a *summary* about the study/project - i.e. how it came about, who is involved, research question, what types of data were delivered, etc.

## Objectives

-   List research objectives here
-   You can use asterisk or dash to make a list

# Data preparation

## Load data

For the demo, we'll just use the mtcars dataset.

```{r cars}
mtcars
```

# Plots and Figures

Output from plotting functions are included.

```{r barplots}
mtcars %>%
  select(mpg, cyl, disp, hp) %>%
  rownames_to_column(var='Model') %>%
  pivot_longer(cols=-Model) %>%
  ggplot(mapping=aes(x=Model,value)) +
  geom_bar(stat='identity') +
  facet_grid(name ~ ., scales='free') + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## 2D and 3D PCA plots {.tabset}

For .html output, you can include 3D interactive plots using `plotly` package.

### 2D PCA

```{r 2D-PCA, warning=FALSE}
res.pca <- prcomp(mtcars)
fviz_pca_ind(res.pca,
             col.ind=as.factor(mtcars$cyl),
             addEllipses = TRUE,
             legend.title='cyl',
             repel=TRUE,
             title='')
```

### 3D PCA

```{r 3D-pca, out.width='600px', out.height='400px'}
plotly_pca(res.pca, as.factor(mtcars$cyl))
```

# Appendix

## Code

```{r all-code, ref.label=knitr::all_labels(), include=TRUE, echo=TRUE, eval=FALSE}

```

## R session info

```{r session-info, include=TRUE}
sessionInfo()
```
